\documentclass[11pt]{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usecolortheme{beaver}
\usepackage{graphicx}
\usefonttheme{structuresmallcapsserif}
\usepackage{times}
\usetheme{Warsaw}
\begin{document}
	\author{Mohammed Althaf T \& Anjusha BJ}
	\title{WORKLORD : Job Portal}
	\begin{frame}[plain]
		\maketitle
	\end{frame} 
	
	\section{ \color{white} INTRODUTION} 
	\frame{\frametitle{\color{black}INTRODUCTION} 
		\hspace*{12pt}
		
		The proposed system ”WORKLORD” is a web based application is to give the job seekers a platform for finding right and satisfactory job according to their qualification and skills. It also connect the job seekers with the major companies. Job portals requires features like profile management,view notifications and other filtering options for both company and users to match with the company/user with their preferred skills.There are many job portals that claims to provide you the best job , but none of them address the issues faced by the new job seekers. Most of portals give higher priority for experienced job seekers.
	}

	\section{SYSTEM ANALYSIS} 
	\frame{\frametitle{\color{black}Existing System}
		\subsection{Existing System}
		\begin{itemize}
			\item Company and User registration.
			\item Users Upload Resume.
			\item Company view Userdetails.
			\item User Search companies and view vacancy.
			
		\end{itemize}	
	}
	
	\frame{\frametitle{\color{black}Proposed System}
		\subsection{Proposed System}
		\begin{itemize}
			\item Company and User registration. 
			\item Users Upload Resume.
			\item Attend Tests and Complete Tasks.
			\item Company view Userdetails and performance in fields.
			\item User Search companies and view vacancy.

		\end{itemize}
		
	}
	\subsection{Module Description}
	\frame{\frametitle{\color{black}User}
		
		\subsubsection{User}
		\begin{itemize}
			\item Register
			\item Login
			\item Attend Tests/Tasks
			\item Edit User details
			\item Change password
			\item View Notifications
			\item View Scores
			\item Contact Admin
	\end{itemize}}
	
	\frame{\frametitle{\color{black}Company}
	
	\subsubsection{Company}
	\begin{itemize}
		\item Register
		\item Login
		\item Edit Company details
		\item Change password
		\item View qualified users
		\item View notifications
		\item Add Vacancies
		\item Contact Admin
\end{itemize}}
	
	
	%\frame{\frametitle{Module Description}\subsection{User}}
	
	\subsection{ Feasibility}
	\frame{\frametitle{\color{black}Technical Feasibility}
		
		\subsubsection{Technical Feasibility}
		\begin{itemize}
			\item System is focused in developing with current limitation.
			\item System can be used anywhere.
			\item User friendly.			 
			\item System can be maintained easily.
	\end{itemize}}
	
	\frame{\frametitle{\color{black}Operational Feasibility}
		
		\subsubsection{Operational Feasibility}
		\begin{itemize}
			\item System will meet the user's and company's requirements. 
			\item The User is not required to have the high technical knowledge. 
			\item No need for any other requirements.
			
	\end{itemize}}
	
	\frame{\frametitle{\color{black}Economic Feasibility}
		
		\subsubsection{Economic Feasibility}
		\begin{itemize}
			\item Not costly for Users.	
			\item Does not cost for development team. 
			\item No additional hardware required than a computer. 
			\item Estimated cost for the system to perform is feasible.  
	\end{itemize}}
	
	\subsection{System Environment}
	\frame{\frametitle{\color{black}Hardware/Software Requirement (Developer)}
		
		\subsubsection{Hardware/Software Requirement (Developer)}
		\begin{itemize}
			\item Processor : Intel Pentium/Celeron or newer	  
			\item RAM: 2GB.	
			\item Storage: 20GB Hard Disk.
			\item Operating System : Linux
	\end{itemize}}
	
	
	\frame{\frametitle{\color{black}Hardware/Software Requirement (Developer)}
		\subsubsection{Hardware/Software Requirement (Developer)}
		\begin{itemize}
			\item Back-end : PHP,MYSQL(Database) 
			\item Front-end : Javascript,Bootstrap,Html,CSS
			\item Text Editor : Gedit
			\item Web server solution : Xampp
			\item Browser : Chrome
			\item Other Utils : Git
	\end{itemize}}
	
	
	\frame{\frametitle{\color{black}User Requirement}
		\subsubsection{User Requirement}
		\begin{itemize}
			\item A Smart Phone or Laptop or Computer.
			\item Internet Access.
	\end{itemize}}

	\frame{\frametitle{}
	\subsubsection{User Requirement}
	\begin{center}
\color{blue} \large THANK YOU
\end{center}}
	
\end{document}